Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-22 paper_comparison/paper_comparison/paper_comparison.Rmd
make better plots for result

---
title: |
  Why aren't significance tests commonly used for linear regression diagnostics?
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
  - name: Susan VanderPlas
    affil: b
    email: susan.vanderplas@unl.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

@@

```{r}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1)) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power")

@@

for (i in target_sigma) {
  j <- j + 1
  plist[[j]] <- 
  VI_MODEL$plot(poly_model(shape = 2, x = rand_uniform())$
                  gen(n = 100, computed = select(mutate(ex_dat, e = sqrt(i) * e), x, e)), theme = theme_light(), 
              remove_axis = TRUE, 
              remove_grid_line = TRUE) +
    ggtitle(round(es[j], 1))
}

patchwork::wrap_plots(plist)
```

@@

```{r eval = FALSE}
vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  facet_wrap(~x_dist)
```

```{r eval = FALSE}
vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  facet_wrap(~x_dist)
```

>>>>

---
title: |
  Why aren't significance tests commonly used for linear regression diagnostics?
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
  - name: Susan VanderPlas
    affil: b
    email: susan.vanderplas@unl.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{lscape}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1)) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power")

@@

for (i in target_sigma) {
  j <- j + 1
  plist[[j]] <- 
  VI_MODEL$plot(poly_model(shape = 2, x = rand_uniform())$
                  gen(n = 100, computed = select(mutate(ex_dat, e = sqrt(i) * e), x, e)), theme = theme_light(base_size =  5), 
              remove_axis = TRUE, 
              remove_grid_line = TRUE) +
    ggtitle(round(es[j], 1))
}

patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(11, .x, 11, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(1, 1, 10, 11), .))
```

@@

\begin{landscape}

```{r fig.height = 3, fig.width = 12, fig.cap="..."}
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(16, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(1, 1, 15, 11), .))
```

```{r fig.height = 3, fig.width = 12, fig.cap="..."}
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(16, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(1, 1, 15, 11), .))
```

\end{landscape}

### 2022-11-22 paper_comparison/paper_comparison/paper_comparison.tex
make better plots for result

\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%

@@

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-7-2} \end{center}

@@

>>>>

\usepackage{lscape}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%

@@

@@

\begin{landscape}

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-8-1}

\caption{...}\label{fig:unnamed-chunk-8}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-9-1}

\caption{...}\label{fig:unnamed-chunk-9}
\end{figure}

\end{landscape}
